\documentclass[12pt]{article}

\usepackage{xcolor} % for different colour comments

%% Comments
\newif\ifcomments\commentsfalse

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\ds}[1]{\authornote{blue}{ND}{#1}}

\begin{document}
\pagenumbering{gobble}
\title{Problem Statement for Smart Waiter} 
\author{Pavneet Jauhal, Shan Perera, Meraj Patel}
\date{\today}

\maketitle

	Many restaurants are starting to incorporate new technology into their dining experience. Specifically, restaurants are moving towards an app based system to allow users to make orders. Some of the ``All You Can Eat'' sushi restaurants have introduced tablets with their own application that allows users to order from their menu. This approach has many limitations. For instance, it is tedious to pass a singular device around the table to make your order. \\
	
	Some of the large food chains have come up with a more diverse solution which allows users to download an app for their restaurant onto their personal smartphone devices. This solution is available for everyone to use from the comfort of their own device. However, the user must learn how to use and interact with every single restaurants app on an individual basis.  For users who are not tech savvy, this solutions is still tedious.\\
	
	Third party applications have attempted to create a singular solution for all restaurants, which is a step in the right direction. For instance, OpenTable is an application which allows you to scroll through many restaurants menus through a singular app. However, there are major limitations to this solution. The application does not allow users to make orders and payments.\\
	
	Thusly, there are few point of sales products on the market that offer a universal solution for multiple restaurants.  The market requires a singular app which allows customers to order and make payments at any restaurant of their choice. Moreover, the app should have a singular UI which will work for all restaurants that the customer visits. Similarly, the user should only be required to create a single account which will work for all restaurants.


\wss{This is an example comment.  You can turn comments off by replacing
  commentstrue by commentsfalse.}

\end{document}








